---
title: "SMART Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: cosmo
    logo: "michigan-logo.png"
    favicon: "michigan-logo.png"
    css: "inst/assets/styles-auth.css"
vertical_layout: fill
runtime: shiny
---

<style>
.navbar-logo.pull-left {
  padding-top:4px;
}
.navbar {
  background-color:#003D79;
  border-color:white;
}
.navbar-brand {
color:white!important;
}

</style>   

<style type="text/css">

.chart-title { /* chart_title */
  font-size: 125%
}

.panel-auth {
    position: fixed;
    top: 0;
    bottom: 0;
    left: 0;
    right: 0;
    background-color: #FFF;
    opacity: 1;
    z-index: 99997;
    overflow-x: hidden;
    overflow-y: scroll;
}

</style>

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(shinymanager)

# define some credentials (you can also use sqlite database)
credentials <- data.frame(
  user = c("dashboard-user"),
  password = c("SMART2023"),
  stringsAsFactors = FALSE
)
```

```{r setup, include=FALSE}
# packages
library(flexdashboard)
library(shiny)
library(plotly)
library(RColorBrewer)
library(stringr)
library(shinythemes)
library(shinyTime)
library(DT)
library(highcharter)
library(readr)
library(ggsankey)

# data and functions
source('redcap-data.R')
source('functions.R')
```

```{r password}
auth_ui(id = "auth")

auth <- callModule(
  module = auth_server,
  id = "auth",
  check_credentials = check_credentials(credentials)
)
```

Screening & Enrollment
================================================================================

Row {data-height=30%}
--------------------------------------------------------------------------------

### Enrolled

```{r out.width = '100%', out.height = '100%'}

valueBox(
  value = sprintf('%i (%.0f%%)', n_enrolled, n_enrolled_percent),
  caption = sprintf('enrolled as of %s', format(Sys.Date(), '%B %d, %Y')),
  color = 'lightgreen',
  icon = 'ion-android-checkbox-outline'
)

```

### Exclusions due to Eligibility

```{r out.width = '100%', out.height = '100%'}

valueBox(
  value = sprintf('%i (%.0f%%)', n_excluded, n_excluded_percent),
  caption = 'excluded due to eligilibity requirements',
  color = 'orange',
  icon = 'ion-ios-flag'
)

```

### Exclusions due to Informed Consent Refusal

```{r out.width = '100%', out.height = '100%'}

valueBox(
  value = sprintf('%i (%.0f%%)', n_refused, n_refused_percent),
  caption = 'refused informed consent',
  color = 'orange',
  icon = 'ion-android-clipboard'
)

```

Row {data-height=70%}
--------------------------------------------------------------------------------

### Reasons for Exclusion {data-width=50%}

```{r out.width = '100%', out.height = '100%'}

colors <- rev(brewer.pal(n = 4, name = 'Blues'))
colors <- c(colors[1], colors[3], colors[2], colors[4])

tm_data <- data_to_hierarchical(
  data = top_exclusion_reasons,
  group_vars = c(reason_class, reason),
  size_var = count,
  colors = colors
)

hchart(
  tm_data,
  type = 'treemap'
)

```

### Patient Enrollment by Month {data-width=50%}

```{r out.width = '100%', out.height = '100%'}

enrollment_plot <- ggplot(data = screening_by_month, aes(fill = type)) +
  geom_bar(aes(x = date, y = count, group = type),
           stat = 'identity',
           position = position_dodge(0.9),
           color = 'black'
  ) +
  scale_fill_brewer(palette = 'Greens') +
  xlab('') + ylab('') +
  theme_bw() +
  theme(
    legend.position = 'none'
  )

ggplotly(enrollment_plot, tooltip = c('x', 'group', 'y'))

```

Treatment Assignment
================================================================================

### Patient Assignment

```{r}

assign_ui <- fillPage(
  br(''),
  # sidebar
  sidebarLayout(
    # randomization
    sidebarPanel(
      title = 'Inputs',
      width = 12,
      textInput(
        inputId = 'id',
        label = 'Patient ID (ex: E003)'
      ),
      radioButtons(
        inputId = 'stage',
        label = 'Stage',
        choices = c('Stage 1', 'Stage 2'),
        selected = 'Stage 1'
      ),
      actionButton(
        inputId = 'submit',
        label = 'Show Assignment')
    ),
    # show current data
    mainPanel(
      dataTableOutput('responses', height = '5.7em'),
      dataTableOutput('datetime', height = '5.7em'),
      width = 12
    )
  )
)

assign_server <- function(input, output, session) {

  # input
  id <- eventReactive(input$submit, input$id)
  stage <- eventReactive(input$submit, input$stage)

  current_time <- eventReactive(input$submit, lubridate::now())

  # retrieve row of interest
  getRow <- reactive({
    return(get_treatment(id(), stage()))
  })

  getTime <- reactive({
    return(current_time())
  })

  # save row to output
  output$responses <- renderDataTable(
    {input$submit
    datatable(
      getRow(),
      rownames = FALSE,
      colnames = c('Patient ID', 'Treatment'),
      options = list(
        paging = FALSE,
        dom = 't'
      )
    )}
  )

  ## save time
  output$datetime <- renderDataTable(
    {input$submit
    datatable(
      data.frame(
        date = as.Date(getTime(), format = "%Y-%m-%d"),
        time = strftime(getTime(), format="%H:%M:%S")
      ),
      rownames = FALSE,
      colnames = c('Date', 'Time (EST)'),
      options = list(
        paging = FALSE,
        dom = 't'
      )
    )}
  )

}

shinyApp(
  ui = assign_ui,
  server = assign_server
)

```

### Treatment Distribution as of `r format(Sys.Date(), "%B %d, %Y")`

```{r, out.width = '100%', out.height = '100%'}

treatment_one_levels <- c(
  'IV Methylprednisolone',
  'Upadacitinib',
  'IV Methylprednisolone + Upadacitinib'
)

treatment_two_levels <- c(
  'Upadacitinib',
  'Cyclosporine',
  'Add IV Methylprednisolone',
  'Switch to IV Methylprednisolone + Cyclosporine',
  'Escalate to IV Methylprednisolone + Upadacitinib',
  'Switch to Cyclosporine Rescue'
)

treatment_distribution <- treatment_distribution %>%
  mutate(
    treatment_one = factor(
      treatment_one,
      levels = treatment_one_levels
    ),
    treatment_two = factor(
      treatment_two,
      levels = treatment_two_levels
    )
  )

count_data <- treatment_distribution %>%
  group_by(treatment_one, treatment_two) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  complete(treatment_one, treatment_two, fill = list(count=0)) %>%
  filter(
    (treatment_one == 'IV Methylprednisolone' & (treatment_two == 'Upadacitinib' | treatment_two == 'Cyclosporine')) |
    (treatment_one == 'Upadacitinib' & (treatment_two == 'Add IV Methylprednisolone' | treatment_two == 'Switch to IV Methylprednisolone + Cyclosporine')) |
    (treatment_one == 'IV Methylprednisolone + Upadacitinib' & (treatment_two == 'Escalate to IV Methylprednisolone + Upadacitinib' | treatment_two == 'Switch to Cyclosporine Rescue')) |
    is.na(treatment_two)
  )

test <- count_data %>%
  make_long(treatment_one, treatment_two, value = count)

counts = count_data$count

treatment_plot <- plot_ly(
  type = 'sankey',
  orientation = 'h',
  node = list(
    label = c(
      'Methylpred',
      'Upa',
      'Methylpred + Upa',
      'Add Upa',
      'Add Cyclo',
      'Not Assigned',
      'Add Methylpred',
      'Switch to Methylpred + Cyclo',
      'Not Assigned',
      'Escalate to Methylpred + Upa',
      'Switch to Cyclo',
      'Not Assigned'
    ),
    color = c('#ea6a47', '#c86cbb', 'skyblue', '#ea6a47', '#ea6a47', '#ea6a47', '#c86cbb', '#c86cbb', '#c86cbb', 'skyblue', 'skyblue', 'skyblue')
  ),
  link = list(
    source = c(0, 0, 0, 1, 1, 1, 2, 2, 2),
    target = c(3, 4, 5, 6, 7, 8, 9, 10, 11),
    value = counts
  ),
  hoverinfo = "text",
)

treatment_plot

```

Assessment Times
================================================================================

### Scheduled Date and Time of Patient Assessments

```{r}

assess_datatable <- datatable(assessment_times)

assess_datatable <- datatable(assessment_times,
  rownames = FALSE,
  colnames = c('ID','Start Time', 'Day 1', 'Day 2', 'Day 3', 'Day 4', 'Day 5', 'Day 6', 'Day 30', 'Day 60', 'Day 90'),
  options = list(
    order = list(2, 'desc'),
    dom = 'ft',
    columnDefs = list(list(visible=FALSE, targets=c(11:19))),
    pageLength = 1000
  )
) %>% formatDate(~start_time + day1 + day2 + day3 + day4 + day5 + day6 + day30 + day60 + day90, method = 'toLocaleString')

for(i in c(1:6, 30, 60, 90)) {

  temp_day_var  = paste0('day', i)
  temp_time_var = paste0('time_until_day', i)

  assess_datatable <- assess_datatable %>%
    formatStyle(
      temp_day_var,
      temp_time_var,
      backgroundColor = styleInterval(c(-6, 6), c('white', '#ff0033', 'white'))
    )

}

renderDataTable(assess_datatable)

```
